\subsection{AP-00: Small Scale Alert Generation Processing}
\label{drp-00}

\subsubsection{Objective}

This test specification demonstrates the successful execution of an
Alert Generation payload on a relatively small scale based on data from
precursor surveys.

It will demonstrate that:

\begin{itemize}

  \item{Science payload code can be made available on systems managed by the
  LSST Data Facility;}

  \item{The science payload can be executed under the
  control of the Offline Processing Execution service;}

  \item{All required science data products can be collected by the execution
  service and made available for subsequent analysis;}

  \item{The Alert Generation payload generates results broadly
  equivalent to ``native'' reductions of precursor survey data.}

\end{itemize}

Note that this test specification does not extend to demonstrating the
detailed compliance of LSST data products with all \citeds[Science
Requirements Document]{LPM-17} level requirements: such a demonstration would
require carefully curated LSST-like datasets (or simulated data), a detailed
understanding of the LSST system, LSST-like calibration products, etc, which
are assumed not to be available for this test.

\subsubsection{Approach refinements}

The general approach defined in \citeds{LDM-503} is used.

\subsubsection{Test case identification}

\begin{longtable} {|p{0.4\textwidth}|p{0.6\textwidth}|}\hline
\textbf{Test Case}  & \textbf{Description} \\\hline

\hyperref[ag-00-00]{AG-00-00} & Tests that the Alert Generation science payload can be installed on LSST Data Facility-managed systems.\\\hline
\hyperref[ag-00-05]{AG-00-05} & Tests the execution of the Alert Generation
payload under the control of the Offline Processing Execution Service.\\\hline
\hyperref[ag-00-10]{AG-00-10} & Tests that required data products are
produced by executing the Alert Generation payload. \\\hline
\hyperref[ag-00-15]{AG-00-15} & Tests that the delivered processed visit images meet scientific requirements. \\\hline
\hyperref[ag-00-20]{AG-00-20} & Tests that the delivered difference images meet scientific requirements. \\\hline
\hyperref[ag-00-25]{AG-00-25} & Tests that the delivered DIASource catalogs meet scientific requirements. \\\hline
\hyperref[ag-00-30]{AG-00-30} & Tests that the delivered DIAObject
	catalog meets scientific requirements. \\\hline
\end{longtable}
